Description of raw CFEC data processing for NCEAS portfolio effects working group

### 2016-03-22 process_raw_data/process_raw_cfec_data.Rmd
bug fix

```{r dataload, warnings=FALSE, message = FALSE}
load("cfec_w_IDs")
cfec = cfecnew
rm(cfecnew) # remove the old named object
```

@@

### Species  
Because of changes in species reporting (examples = rockfish, the use of unidentified species), we need to do some lumping some species. Groupings were consistent to be consistent with the ADFG codes, so for example rockfish are grouped into a 'pelagic', 'demersal', and 'slope' group.  
```{r specLump}

@@

# number fish tickets sequentially
cfec$f_ticket = seq(1, dim(cfec)[1])
cfec$F_PERMIT = as.numeric(as.factor(cfec$F_PERMIT))
```

>>>>

```{r dataload, warnings=FALSE, message = FALSE}
load("cfec_w_IDs")
cfec = cfecnew
rm(cfecnew) # remove the old named object

# Remove A80 and CP vessels
A80<-c(68870,29923,22011,39798,59870,8500,41219,62545,56965,54693,1119,57228,69038,61081,61083,55921,57211,56964,36202,43260,54392,51873,48183,55767)
CP <-c(56987,59378,57621,59170,55767,57450,54886,56991,60407,60795,60202,60660,56789,56618,59503)
cfec <- filter(cfec,!adfg %in% c(A80,CP))
```

@@

### Species  
Because of changes in species reporting (examples = rockfish, the use of unidentified species), we need to do some lumping some species. Groupings were consistent to be consistent with the ADFG codes, so for example rockfish are grouped into a 'pelagic', 'demersal', and 'slope' group.  
```{r specLump}
cfec$specn.orig = cfec$specn

@@

# number fish tickets sequentially
cfec$f_ticket = as.numeric(as.factor(cfec$f_ticket))
cfec$F_PERMIT = as.numeric(as.factor(cfec$F_PERMIT))
```
